Species motif participation provides unique information about species risk of extinction

### 2022-06-19 manuscript/reorder_main_text.tex
Updates from Overleaf

        \begin{figure}[hb!]
        \centering
        \includegraphics[width=1.0\textwidth]{figures/concept_fig_ver2.eps}
        \caption{Conceptual figure of a toy food web. \textbf{a)} This food web contains examples of the four motifs: apparent competition (blue), three-species chain (purple), omnivory (green), and direct competition (yellow). These motifs capture different ways in which disturbances to basal resources can propagate through the network. For example, a disturbance to the bottom species in a three-species chain will have a direct effect on the middle species but only indirectly affect the top species while a disturbance to the bottom species in an omnivory motif will have a direct effect on the middle species and direct and indirect effects on the top species. 
        Note that the nodes participate in more motifs than the ones highlighted. \textbf{b)} In the same food web, species with identical degree and trophic level can have different motif participation; here species A (light grey node with links in the same motif colored light grey) participates in only two chains while species B (dark grey node with its direct consumption links colored dark grey) participates in chains more than tree times more frequently (see inserted table for counts of participation in all four motifs). 
        Despite having equal degree and trophic level, species A may be at greater risk of going extinct than species B because of its dependence on specialist prey species. Two-thirds of the prey of species B are generalists and therefore more likely to survive a disturbance to basal resources. By including information about indirect interactions, motif profiles reflect this difference between species A and B while trophic level and degree do not.}
    \label{fig:concept}
    \end{figure}

>>>>

        \begin{figure}[hb!]
        \centering
        \includegraphics[width=1.0\textwidth]{figures/concept_fig_ver2.eps}
        \caption{Conceptual figure of a toy food web. \textbf{a)} This food web contains examples of the four motifs: apparent competition (blue), three-species chain (purple), omnivory (green), and direct competition (yellow). These motifs capture different ways in which disturbances to basal resources can propagate through the network. For example, a disturbance to the bottom species in a three-species chain will have a direct effect on the middle species but only indirectly affect the top species while a disturbance to the bottom species in an omnivory motif will have a direct effect on the middle species and direct and indirect effects on the top species. 
        Note that the nodes participate in more motifs than the ones highlighted. \textbf{b)} In the same food web, species with identical degree and trophic level can have different motif participation; here species A (light grey node with links in the same motif colored light grey) participates in only two chains while species B (dark grey node with its direct consumption links colored dark grey) participates in chains more than three times more frequently (see inserted table for counts of participation in all four motifs). 
        Despite having equal degree and trophic level, species A may be at greater risk of going extinct than species B because of its dependence on specialist prey species. Two-thirds of the prey of species B are generalists and therefore more likely to survive a disturbance to basal resources. By including information about indirect interactions, motif profiles reflect this difference between species A and B while trophic level and degree do not.}
    \label{fig:concept}
    \end{figure}
